Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-26 Arxiv/main.tex
fix typos in proof

\begin{lem}
\label{lem_score_pro_eq}
  Given $\hexpmech(\dataobs)$ and $r', r'' \in \candidateset{\dataobs}$, then following holds:
  $$
  \ux{r'} = \ux{r''} \iff \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}.
  $$  
\end{lem}
\begin{proof} of Lemma \ref{lem_score_pro_eq}.
\begin{itemize}
  \item $\implies$
  \begin{equation*}
  \begin{split}
  & \ux{r'} = \ux{r''} \\
  & Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r):\\
  & \implies \hellinger(\bysinfer(\dataobs), r') = \hellinger(\bysinfer(\dataobs), r'') \\
  & \implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r'')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}\\
  & Apply\ Definition\ \ref{def_smoo} :\\
  & \implies \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}.
  \end{split}
  \end{equation*}

@@

    \begin{equation*}
  \begin{split}
  & \hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''} \\
  & Apply\ Definition\ \ref{def_smoo} :\\
  & \implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r'')}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}\\
  & \implies  \hellinger(\bysinfer(\dataobs), r') = \hellinger(\bysinfer(\dataobs), r'') \\
  & Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r):\\
  & \implies \ux{r'} = \ux{r''}.
  \end{split}
  \end{equation*}
\end{itemize}

@@

\begin{definition}
\label{def_cardinality}
  $\cardinality{\dataobs}{r}$

  Define $\cardinality{\dataobs}{r}$ as the cardinality of $R_r$ s.t. $ R_r = \{ r' | r' \in \candidateset{\dataobs}\ s.t. \ \ux{r'} = \ux{r}, \}$ and $\forall \hat{r} \in \candidateset{\dataobs}, \hat{r} \notin R_r \implies \ux{\hat{r}} \neq \ux{r}$, 
\end{definition}

\begin{lem}
\label{lem_score_pro_convert}
 Given $\hexpmech(\dataobs)$, then the following property holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}
 \end{equation*}
\end{lem}
\begin{proof} of Lemma \ref{lem_score_pro_convert}.\\
To compute $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}$\\
$\iff $ to compute $\hexpmechPr{\dataobs}{ R | R = \{r' | r' \in \candidateset{\dataobs} \land \ux{r'} = \ux{r}\}}.$\\
By Definition \ref{def_cardinality}, $R_r$ is this set.\\
$\implies \hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \hexpmechPr{\dataobs}{R_r} $.\\
By the independence of $r' \in R_r$, $ \hexpmechPr{\dataobs}{z \in R_r}  =\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'}$ ,\\
Apply Lemma \ref{lem_score_pro_eq} in $R_r$, \\
$\implies$ for any $r', r''\in R_r$, $\hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}$.\\
$\implies$ $\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
$\implies$ $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
\end{proof}

@@

Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. In Beta-binomial system, let $\epsilon\geq 0$ and $\ux{r} + k >=0$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
\leq
e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}.
\end{equation*}
\end{lem}

@@

\noindent \textbf{Dilation Property of $\hexpmech$}
\begin{lem}
\label{lem_dilation}
Given $\hexpmech(\dataobs)$ in Beta-binomial system, let $\lambda < |\gamma|$, $\epsilon$, $|\delta'| < 1$ and $\gamma \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset{\dataobs}|})})$, the dilation property holds:

\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
\leq
e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}} + \frac{\delta'}{2}.
\end{equation*}
\end{lem}

@@

  In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$:
  \begin{itemize}
    \item[-] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$,  $R_r$ containing only the correct posterior.
    \item[-] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
  \end{itemize}
  Let $\ux{t} = e^{\lambda} \ux{r}$, then the proof is given by cases:

  \begin{itemize}
    \item {\boldmath$\ux{r} = 0$}:

@@

    \item {\boldmath$\ux{r} \neq 0$}:\\
        By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$.\\
        By $\ux{t} = e^{\lambda} \ux{r} \neq 0$, $\cardinality{\dataobs}{t} = 2$.

@@

        By $\cardinality{\dataobs}{t} = \cardinality{\dataobs}{r} = 2$, we need to show:
        \begin{equation*}
        \hexpmechPr{\dataobs}{z = r}
        \leq
        e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{z = t},
        \end{equation*}
        holds with failure probability $\frac{\delta'}{2}$.

@@

        \item {\boldmath$\lambda > 0$}:

@@

          We need to show:
          \begin{equation*}
          \label{eq_dilation_case2}
          \ux{r}
          \leq 
          \frac{S(\dataobs)}{(1 - e ^ {\lambda})},
          \end{equation*}         
          holds with failure probability $\frac{\delta'}{2}$.

@@

          apply this bound to eq. \ref{eq_dilation_case2}:
          \begin{equation*}
          \begin{split}
          Pr[\ux{r} \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] 
          & = |\candidateset{\dataobs}|exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
          & = |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}).\\
          \end{split}
          \end{equation*}

          By setting $|\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}) = 1 - \frac{\delta'}{2}$, 
          \begin{equation*}
          \begin{split}
          Pr[\ux{r} \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] = 1 - \frac{\delta'}{2}
          \end{split}
          \end{equation*}
          holds, i.e.,
          \begin{equation*}
          \label{eq_dilation_case2}
          \ux{r}
          \leq 
          \frac{S(\dataobs)}{(1 - e ^ {\lambda})},
          \end{equation*}         
          holds with failure probability $\frac{\delta'}{2}$ is proved.

@@

      Apply Definition \ref{def_smoo} and $\uxadj{r} = \hellinger(\bysinfer(\dataobs'),r)$ for $r \in \candidateset{\dataobs'}$:\\
      \begin{equation*}
      \begin{split}          
      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
      \big( e^{\frac{\epsilon}{2}}
      \cardinality{\dataobs}{t}  \hexpmechPr{\dataobs'}{z = r} \\
      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
      \big ) \Big)\\
      & = \frac{\cardinality{\dataobs}{t}}{\cardinality{\dataobs}{r}} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}
      \hexpmechPr{\dataobs'}{z = r} \\
      & + \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{\cardinality{\dataobs}{r}}
      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big).
      \end{split}
      \end{equation*}

      Then, $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where $\epsilon' = \frac{\cardinality{\dataobs}{t}}{\cardinality{\dataobs}{r}} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}$, and
      $\delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{\cardinality{\dataobs}{r}}
      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big)$.

@@

      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
      $$
      \epsilon' = \ln( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}),
      $$ and
      $$
      \delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big).
      $$

@@

      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
      $$
      \epsilon' = \ln (2 \cdot e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}),
      $$ and
      $$
      \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big).
      $$

@@

      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
      $$
      \epsilon' = \ln (\frac{1}{2} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}),
      $$ and
      $$
      \delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big).
      $$

    \item {\boldmath$\ux{r} = 0$, $\uxadj{r} = 0$}:
      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 1$ under data set $\dataobs$.

@@

      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
      $$
      \epsilon' = \ln (e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}),
      $$ and
      $$
      \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big).
      $$

@@

      Then, $\hexpmech$ is $(\epsilon', \delta)-$differential privacy, by setting $\epsilon $ and $\delta$ as the maximum value from above.
      i.e., under the case {\boldmath$\ux{r} = 0$, $\uxadj{r} \neq 0$}, 
      $
      \epsilon' = \ln (2 \cdot e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}})
      $, and
      $
      \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) \Big).
      $
\end{proof}

>>>>

\begin{lem}
\label{lem_score_pro_eq}
  Given $\hexpmech(\dataobs)$ and arbitrary $r_1, r_2 \in \candidateset{\dataobs}$, then following holds:
  $$
  \ux{r_1} = \ux{r_2} \iff \hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2}.
  $$  
\end{lem}
\begin{proof} of Lemma \ref{lem_score_pro_eq}.
\begin{itemize}
  \item $\implies$
  \begin{equation*}
  \begin{split}
  & \ux{r_1} = \ux{r_2} \\
  & Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r)\ for\ r \in \candidateset{\dataobs}:\\
  & \implies \hellinger(\bysinfer(\dataobs), r_1) = \hellinger(\bysinfer(\dataobs), r_2) \\
  & \implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_1)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_2)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}\\
  & Apply\ Definition\ \ref{def_smoo} :\\
  & \implies \hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2}.
  \end{split}
  \end{equation*}

@@

    \begin{equation*}
  \begin{split}
  & \hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2} \\
  & Apply\ Definition\ \ref{def_smoo} :\\
  & \implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_1)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_2)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}\\
  & \implies  \hellinger(\bysinfer(\dataobs), r_1) = \hellinger(\bysinfer(\dataobs), r_2) \\
  & Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r)\ for\ r \in \candidateset{\dataobs}:\\
  & \implies \ux{r_1} = \ux{r_2}.
  \end{split}
  \end{equation*}
\end{itemize}

@@

\begin{definition}
\label{def_cardinality}
  $\cardinality{\dataobs}{r}$, $R^{\dataobs}_r$.

  Given $\hexpmech(\dataobs)$, define $R^{\dataobs}_r \subset \candidateset{\dataobs}$, s.t. $r' \in R^{\dataobs}_r \iff \ux{r'} = \ux{r}$.

  Given $\hexpmech(\dataobs)$, define $\cardinality{\dataobs}{r}$ as the cardinality of $R^{\dataobs}_r$. 
\end{definition}

\begin{lem}
\label{lem_score_pro_convert}
 Given $\hexpmech(\dataobs)$, then the following property holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}
 \end{equation*}
\end{lem}
\begin{proof} of Lemma \ref{lem_score_pro_convert}.\\
To compute $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}$\\
$\iff $ to compute $\hexpmechPr{\dataobs}{ z \in R | R = \{r' | r' \in \candidateset{\dataobs} \land \ux{r'} = \ux{r}\}}.$\\
By Definition \ref{def_cardinality}, $R^{\dataobs}_r$ is this set.\\
$\implies \hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \hexpmechPr{\dataobs}{z \in R^{\dataobs}_r} $.\\
By the independence of $r' \in R_r$, $ \hexpmechPr{\dataobs}{z \in R_r}  =\sum\limits_{r'\in R^{\dataobs}_r} \hexpmechPr{\dataobs}{z = r'}$ ,\\
Apply Lemma \ref{lem_score_pro_eq} in $R_r$, \\
$\implies$ for any $r', r''\in R_r$, $\hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}$.\\
$\implies$ $\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
$\implies$ $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
\end{proof}

@@

Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. In Beta-binomial system, for any $r\in \candidateset{\dataobs}$, let $\epsilon\geq 0$ and $\ux{r} + k \geq 0$, the following \emph{sliding property} holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
\leq
e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}.
\end{equation*}
\end{lem}

@@

\noindent \textbf{Dilation Property of $\hexpmech$}
\begin{lem}
\label{lem_dilation}
Given $\hexpmech(\dataobs)$ in Beta-binomial system, for any $r\in \candidateset{\dataobs}$, let $\lambda < |\gamma|$, $\epsilon$, $|\delta'| < 1$ and $\gamma \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset{\dataobs}|})})$, the following \emph{dilation property} holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
\leq
e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}} + \frac{\delta'}{2}.
\end{equation*}
\end{lem}

@@

  In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$:
  \begin{itemize}
    \item[-] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$,  $R_r$ containing only the correct posterior.
    \item[-] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
  \end{itemize}
  Let $\ux{t} = e^{\lambda} \ux{r}$.

  \begin{assert}
  \label{cardinality_eq}
  For any $r\in \candidateset{\dataobs}$, $\cardinality{\dataobs}{r} = \cardinality{\dataobs}{t}$.
  \end{assert}

  \begin{proof} of Assertion \ref{cardinality_eq}.

  The proof is given by cases:
  \begin{itemize}
    \item {\boldmath$\ux{r} = 0$}:

@@

    \item {\boldmath$\ux{r} \neq 0$}:\\
        By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$.\\
        By $\ux{t} = e^{\lambda} \ux{r} \neq 0$, $\cardinality{\dataobs}{t} = 2$.
  \end{itemize}

  Then, in either case, $\cardinality{\dataobs}{r} = \cardinality{\dataobs}{t}$.

@@

        By Assertion \ref{cardinality_eq}, we need to show:
        \begin{equation*}
        \hexpmechPr{\dataobs}{z = r}
        \leq
        e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{z = t},
        \end{equation*}
        holds with failure probability $\frac{\delta'}{2}$.

@@

        \item {\boldmath $\lambda > 0$}:

@@

          We need to show:
          \begin{equation}
          \label{eq_dilation_case2}
          \ux{r}
          \leq 
          \frac{S(\dataobs)}{(1 - e ^ {\lambda})},
          \end{equation}         
          holds with failure probability $\frac{\delta'}{2}$.

@@

          apply this bound to Equation. \ref{eq_dilation_case2}:
          \begin{equation*}
          \begin{split}
          Pr[\ux{r} \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] 
          & = |\candidateset{\dataobs}|exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
          & = |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}).\\
          \end{split}
          \end{equation*}

          By setting $|\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}) = 1 - \frac{\delta'}{2}$, 
          \begin{equation*}
          \begin{split}
          Pr[\ux{r} \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] = 1 - \frac{\delta'}{2}
          \end{split}
          \end{equation*}
          holds, i.e.,
          \begin{equation*}
          \ux{r}
          \leq 
          \frac{S(\dataobs)}{(1 - e ^ {\lambda})},
          \end{equation*}         
          holds with failure probability $\frac{\delta'}{2}$ is proved.

@@

      Apply Definition \ref{def_smoo} and $\uxadj{r} = \hellinger(\bysinfer(\dataobs'),r)$ for $r \in \candidateset{\dataobs'}$:\\
      \begin{equation*}
      \begin{split}          
      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
      \big( e^{\frac{\epsilon}{2}}
      \cardinality{\dataobs}{t}  \hexpmechPr{\dataobs'}{z = r} \\
      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
      \big ) \Big)\\
      & = \frac{\cardinality{\dataobs}{t}}{\cardinality{\dataobs}{r}} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}}
      \hexpmechPr{\dataobs'}{z = r} \\
      & + \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{\cardinality{\dataobs}{r}}
      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \big) }) \Big).
      \end{split}
      \end{equation*}

      Then, $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where $\epsilon' = \ln \Big( \frac{\cardinality{\dataobs}{t}}{\cardinality{\dataobs}{r}} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big)$, and
      $\delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{\cardinality{\dataobs}{r}}
      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))}\big)}) \Big)$.

@@

      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
      $$
      \epsilon' = \ln \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
      $$ and
      $$
      \delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \Big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
      $$

@@

      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
      $$
      \epsilon' = \ln \Big( 2 \cdot e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
      $$ and
      $$
      \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))}\Big) }) \Big).
      $$

@@

      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
      $$
      \epsilon' = \ln \Big( \frac{1}{2} e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
      $$ and
      $$
      \delta = \frac{e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}}{2}
      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
      $$

    \item {\boldmath$\ux{r} = 0$, $\uxadj{r} = 0$}:

      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 1$ under data set $\dataobs$.

@@

      Apply  $\cardinality{\dataobs}{r} = 1$ and  $\cardinality{\dataobs}{t} = 1$:

      $\hexpmech$ is $(\epsilon', \delta)-$differential privacy where:
      $$
      \epsilon' = \ln \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}} \Big),
      $$ and
      $$
      \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \Big( 1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \Big)}) \Big).
      $$

@@

      Then, $\hexpmech$ is $(\epsilon', \delta)-$differential privacy, by setting $\epsilon $ and $\delta$ as the maximum value from above.
      i.e., under the case {\boldmath$\ux{r} = 0$, $\uxadj{r} \neq 0$}, 
      $
      \epsilon' = \ln (2 \cdot e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} \cdot e^{\frac{\epsilon}{2}})
      $, and
      $
      \delta = e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)}
      \Big( 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 \big(1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))} \big)}) \Big).
      $\\
